\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64

### 2024-01-14 article.tex
Add debugger harness section again

\subsection{Test Suite and  Framework}

@@

@@

Fannkuch-redux involves a permutation algorithm that has a non-trivial algorithmic complexity. It requires both recursion and iterative processes, making it a good test for a language's ability to handle complex computations efficiently.
The fannkuch algorithm is

>>>>

\subsection{Test suite/framework}

@@

\subsubsection{Debug Harness}

A more elaborate way of asserting correctness of translation is to assert that there are no effects except for those intended. One way of achieving this is to check if a sequence of x86 instructions representing a single LLVM-{}- operation change any values except those expected.  An approach to this is to insert a breakpoint before every LLVM-{}- instruction, then attach a debugger that breaks on these,  and ensure that only the intended registers are altered.

To achieve this, only a few changes need to be made to the codebase. A debug flag is introduced, which inserts a label before every instruction by adding a \lstinline!Breakpoint! variant of the \lstinline!ins! type before the assembly emitted of that specific operation. A unique identifier as well as a list of changes expected to be made is encoded. 
This includes a bitmask of GPRs that can possibly be changed (aside from the scratch registers of course) as well as which parts of the stack may be modified. % TODO: implement the stack checker
In addition to this, each of the labels are output with a \lstinline!.globl! directive in the file header. A file is built with these extra symbols using the \lstinline!-d! flag.

Unfortunately, this was never made to work in practice, but the \texttt{harness.py} script is attached regardless. It was made and tested with \texttt{clang16} in mind on Linux.

@@

Fannkuch-redux involves a permutation algorithm that has a non-trivial algorithmic complexity. %It requires both recursion and iterative processes, making it a good test for a language's ability to handle complex computations efficiently.
It stems from the Benchmarks game 
It was made for the Debian benchmarks game 
The fannkuch algorithm is
